Plots

### 2024-11-25 Archive/Plots.Rmd
No changes

```{r}
library(gridExtra)
rank_scatter <- grid.arrange(men_19, women_19, men_22,women_22, men_23, women_23, ncol = 2)
ggsave(filename = "RankScatterPlots.pdf", path = "../Manuscript", plot=rank_scatter, height = 7.5, width = 7)
```

>>>>

```{r}
library(gridExtra)
rank_scatter <- grid.arrange(men_22, women_22, men_19,women_19, men_23, women_23, ncol = 2)
ggsave(filename = "RankScatterPlots.pdf", path = "../Manuscript", plot=rank_scatter, height = 7.5, width = 7)
```
